---
title: "TidyTuesday"
author: "Zaki"
date: "10/11/2020"
output: html_document
---

# 2020 Week 46


## Pre-processing


Load the data

```{r}
# Get the Data

# Read in with tidytuesdayR package 
# Install from CRAN via: install.packages("tidytuesdayR")
# This loads the readme and all the datasets for the week of interest

# Either ISO-8601 date or year/week works!

#tuesdata <- tidytuesdayR::tt_load('2020-11-10')
tuesdata <- tidytuesdayR::tt_load(2020, week = 46)

raw_mobile <- tuesdata$mobile
```




## Load library

```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(countrycode)
library(janitor)
```


## Begin data exploration

```{r}
mobile_df <- tuesdata$mobile
land_df <- tuesdata$landline

# More data points in the landline dataset
dim(mobile_df)
dim(land_df)
```


Make a unique collumn to combine these two

```{r}
mobile_df <- mobile_df %>%
  mutate(Uniq = paste(entity,year, sep="_")) 

land_df_sub <- land_df %>%
  mutate(Uniq = paste(entity,year, sep="_")) %>%
  select(Uniq, landline_subs)

# Combine
df_comb <- mobile_df %>%
  dplyr::left_join(land_df_sub) 
  
```

Plot the number of landline subscription and mobile subscription across time

```{r}
# Number of landline across time
ggplot(df_comb, aes(x=year, y =landline_subs)) +
  geom_smooth() +
  facet_wrap(~continent) +
  scale_y_continuous(limits=c(0,100))

# Number of mobile across time
ggplot(df_comb, aes(x=year, y =mobile_subs)) +
  geom_smooth() +
  facet_wrap(~continent) +
    scale_y_continuous(limits=c(0,100))
```



Plot the number of landline subscription and mobile subscription side by side

```{r,eval=FALSE}
# Calculate differences between the number of subscription per 100 people
df_comb <- df_comb %>%
  mutate(Diff = mobile_subs - landline_subs,
         Categ = if_else(Diff < 0, "MoreLand", "MoreMobile"))


ggplot(df_comb, aes(x=year, y =Diff, colour=Categ)) +
  geom_smooth() +
  facet_wrap(~continent) +
    scale_y_continuous(limits=c(-100,100))
```

Convert data to long format using `pivot_longer`

```{r}
# Make either the landline or mobile negative
df_comb2 <- df_comb %>%
  mutate(landline_subs = landline_subs *-1)

df_comb_long <- df_comb2 %>%
  pivot_longer(c(mobile_subs,landline_subs),
               names_to = "subscription", values_to = "count")
  
```



Plot the number of landline subscription and mobile subscription side by side

```{r}
ggplot(df_comb_long, aes(x=year, y=count, fill=subscription)) +
  geom_bar(stat="identity") +
  #geom_smooth() +
  facet_wrap(~continent) +
    scale_y_continuous(limits=c(-100,100))

# Plot above is not correct because it take the sum of all the continent

```

So we summarise the data. There are some NA, so we exclude these

```{r}
df_sum <- df_comb_long %>%
  select(continent, subscription, count, year) %>%
  na.omit() %>%
  group_by(continent, subscription, year) %>%
  summarize(MeanCount = mean(count))
```

Redo the plot above

```{r}
ggplot(df_sum, aes(x=year, y=MeanCount, fill=subscription)) +
  geom_bar(stat="identity") +
  #geom_smooth() +
  facet_wrap(~continent) +
    scale_y_continuous(limits=c(-150,150)) +
  NULL
```

Highlight which year the number of mobile subscription exceedes landline

```{r}
df_comb3 <- df_comb %>%
  # If the difference is <0 means more landline subscription
  mutate(Diff = mobile_subs - landline_subs) %>%
  select(continent, Diff, year) %>%
  na.omit() %>%
  group_by(continent, year) %>%
  summarize(MeanDiff = mean(Diff)) %>%
  # Select when there are more mobiles subscription (ie Diff >0)
  filter(MeanDiff > 0) %>%
  # Slect the first year this happens
  summarize(MinYear = min(year))   %>%
  mutate(subscription ="landline_subs")
  
```

Repeat plot with the vertical line

```{r}
p <-
  ggplot(df_sum, aes(x=year, y=MeanCount, fill=subscription)) +
  geom_bar(stat="identity") +
  #geom_smooth() +
  facet_wrap(~continent) +
    scale_y_continuous(limits=c(-150,150)) +
  scale_fill_manual(values=c("#729ECE", "#ffb1b7")) +
  #geom_vline(data= df_comb3, aes(xintercept=MinYear)) +
  geom_segment(data= df_comb3, 
               aes(x=MinYear+0.5,
                   y=-100,
                   xend=MinYear+0.5,
                   yend=100),
               linetype="dashed", colour="grey50") +
  geom_text(data= df_comb3, aes(x=MinYear, y=120, label=MinYear)) +
  NULL


# Let's create an additional data frame to hold the text annotations:
dat_text <- data.frame(
  label = c("Mobile", "", "", "Mobile", ""),
  continent   = unique(df_sum$continent),
  subscription ="landline_subs"
)

# Let's create an additional data frame to hold the text annotations:
dat_text2 <- data.frame(
  label = c("Landline", "", "", "Landline", ""),
  continent   = unique(df_sum$continent),
  subscription ="landline_subs"
)

p2 <- 
p + 
  geom_text(
  data    = dat_text,
  mapping = aes(x = 1990, y = 80, label = label),
  size=4, angle=90, colour="#ffb1b7") +
  geom_text(
  data    = dat_text2,
  mapping = aes(x = 1990, y = -80, label = label),
  size=4, angle=90, colour="#729ECE") +
  theme_bw() +
  scale_y_continuous(limits=c(-150,150),
                     breaks = c(-100, 0, 100),
                     label = c("100", "0", "100")) +
  theme(legend.position = "none") +
  labs(
    title = "Adoption of fixed mobile or landline telephone across continent",
    subtitle = "By 2001, mobile phone subscriptions overtakes landline subscriptions in most continents. \nVertical dashed line indicates the year mobile phone subscriptions overtakes landline subscriptions",
    caption = "Source: Pew Research Smartphone Adoption | @zaki_wilmot") +
  ylab("Fixed mobile /landline subscriptions (per 100 people)") +
  NULL
```

Save plot

```{r}
ggsave("~/Desktop/plot.png", p2, width = 11, height = 7,dpi=1000)
```


